DeepSphere: a graph-based spherical CNN

### 2019-11-15 rebuttal.md

# ICLR'20 rebuttal

## General comment about revised manuscript

We uploaded an improved manuscript thanks to the reviewers' comments.

The main update is the addition of theorem 3.2 that formalizes the relation between theorem 3.1 and rotation equivariance. Small changes across the text have been made to clarify the exposition further.

A link to a public git repository containing all the code will be added after the blind-review process.

### 2019-11-20 rebuttal.md

Ref.
1. Semi-Supervised Classification with Graph Convolutional Networks. ICLR'17.
2. Covariant Compositional Networks For Learning Graphs. ICLR'18

### Answer

Thank you for your interest and questions.

1. The two-parameter variant of GCN is ChebNet with a polynomial order of P=1. The method scales linearly with P, and that is an hyper-parameter to be set (analogous to the kernel size in classical CNNs). Note that the single-parameter variant of GCN doesn't fit our theory as we rely on the convergence of the operator to the Laplace-Beltrami to prove its equivariance.

2. What should be predictable and revertible is the transformation applied to the output activations given a transformation applied to the input activations. In our case, both transformations are 3D rotations.
That is, if the input activations are rotated by R, the output will be rotated by the same R.

### 2020-02-14 main.tex
rotation matrix in regular font
Revert "comment todos for submission"
This reverts commit 72052dcf02c1c9492d34b1c65a4832360cf6ade3.
update todos

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\renewcommand{\b}[1]{{\bm{#1}}}  % bold symbol
\newcommand{\bO}{\mathcal{O}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\S}{\mathbb{S}}
\newcommand{\G}{\mathcal{G}}  % graph
\newcommand{\V}{\mathcal{V}}  % vertex set
\newcommand{\E}{\mathcal{E}}  % edge set
\newcommand{\laplacian}{\Delta_{\mathbb S^2}}
\newcommand{\Rg}{\mathcal{R}(g)}
\newcommand{\seminorm}[1]{\left|#1\right|}
\newcommand{\Ln}{\hat L_n^{t_n}}

@@

\todo{
TODO:
\begin{itemize}
	\item Unify vocabulary and avoid synonyms.
		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
		Signal, maps, fields, functions.
		Irregular, uneven, non-uniform.
		Coarsening, down-sampling.
		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
	\item check English vs American English
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
\end{itemize}
}

\todo{
rebuttal:
\begin{itemize}
    \item answer commenter
	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
	\item Show the three samplings in a figure?
	\item better abstract (Friday's talk abstract?)
	\item conclusion: less speculation?
	\item check feedback from ICLR'20 LTS2 reading group
	\item \mdeff{check my Telegram notes}
	\item argue against more generality
	\item figure that show the three samplings? (suggested by reviewer \#2)
\end{itemize}
}

>>>>

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{prop}{Proposition}
\newtheorem*{remark}{Remark}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\renewcommand{\b}[1]{{\bm{#1}}}  % bold symbol
\newcommand{\bO}{\mathcal{O}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\S}{\mathbb{S}}
\newcommand{\G}{\mathcal{G}}  % graph
\newcommand{\V}{\mathcal{V}}  % vertex set
\newcommand{\E}{\mathcal{E}}  % edge set
\newcommand{\laplacian}{\Delta_{\mathbb S^2}}
\newcommand{\Rg}{R(g)}
\newcommand{\seminorm}[1]{\left|#1\right|}
\newcommand{\Ln}{\hat L_n^{t_n}}

@@

\todo{
TODO:
\begin{itemize}
	\item Unify vocabulary and avoid synonyms.
		Sampling, grid, discretization, pixelization $\Rightarrow$ sampling (sampling schemes when not a particular set of vertices?)
		Signal, maps, fields, functions.
		Irregular, uneven, non-uniform.
		Coarsening, down-sampling.
		Sample, vertex, node, pixel, point $\Rightarrow$ vertex
	\item check English vs American English
	\item put all the code (learning experiments from Frédérick and equivariance experiments from Martino) in a common reproducible git repository to be linked from the paper
	\item update pygsp and merge sphere branch
	\item Compute the invariance error of the whole NNs (before and after training, invariance can be learned). Add it with equivariance error of the convolution to \tabref{cosmo}. \nati{I guess we are not doing that}
	\item insert \citet{jiang2019sphericalcnn} in intro: Need a global coordinate system (ok for planets, not projections like cosmo)
	\item mention that \citep{esteves2018sphericalcnn} and \citep{cohen2018sphericalcnn} computed equivariance error
	\item add somewhere (intro?): exploit symmetries to reduce sample cost $\Rightarrow$ we don't discuss symmetries much
	\item \citet{mudigonda2017climateevents} use Integrated Water Vapor (IWV) only. That most probably is the same as our TMQ, which is most probably the most informative feature. TODO: run ours with TMQ alone.
	\item Show the three samplings in a figure?
	\item better abstract (Friday's talk abstract?)
	\item abstract: tackle impactful / important problems in cosmology and climatology (Earth sciences)
	\item conclusion: less speculation?
	\item check feedback from ICLR'20 LTS2 reading group
	\item \mdeff{check my Telegram notes}
	\item argue against more generality
	\item figure that show the three samplings? (suggested by reviewer \#2)
	\item add the eigenfunction alignment in the appendix
	\item Shouldn't theorem 3.2 be a corollary?
	\item Experiments: organize per problem or desideratum?
	\item Articulate the story around the desiderata. Add "most general / powerful" as one (for isotropy).
	\item Better motivate the method (i.e., don't present our work as just the analysis of one method). Why is it a good method? It allows for a linear time implementation of operators on scalar fields. Need to show that functions of the Laplace-Beltrami $h(\Delta)$ can indeed implement any equivariant (gauge invariant \citep{cohen2019gauge}) linear operations on scalar fields. Restructure the method section to show how the cost is reduced to $\bO(pkn)$: (i) discretization ($n$ vertices), (ii) sparsification ($k$ neighbors), (iii) reduction of the class of operators / filters (polynomial order $p$).
	\item A filter operating on scalar fields has to be isotropic / directionless to be equivariant \citep{cohen2019gauge}) [Kondor CCN]
		A cheap solution: if the domain can be globally oriented (e.g., by gravity for 2D or omnidirectional images), then the spatial dimension can be factorized (think of the up, down, right, left directions in 2D images). The sphere could be factorized has two oriented lines for the vertical axis, and a circle horizontally. That is exploited by Khasanova to create anisotropic filters on the sphere for omnidirectional imaging. That of course reduces the symmetry group the NN is to be equivariant to.
		Otherwise there is a price to pay.
		If not but the domain has global symmetries, activations can be lifted to the symmetry group \citep{cohen2018sphericalcnn} [Kondor CCN]. That is however memory and computationally expensive, as the activations must have the size of the symmetry group.
		Without global symmetries, tensor activations are needed \citep{cohen2019gauge}.
	\item Paragraph about cost reduction strategies (discretize, sparsify, polynomial). C.f. notes.
	\item Write why we don't tackle omnidirectional imaging. Same reason as images. Factor the manifold. For some samplings their graph discretization can be factored, yielding anisotropic filters. (c.f. answer to reviewer 1)
}
